---
title: 'BM424 workshop: infectious disease outbreak control'
author: "Morgan Feeney"
date: "17/03/2023"
output: 
  bookdown::html_document2:
    toc: true
    toc_float:
      toc_collapsed: false
    number_sections: false 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(knitr)


city_name <- "Baltyre" ##replace all instances of "Baltyre" with new scenario name
hospital_name <- "Queen's College" ##replace all instances of "Queen's College" with new scenario name
dis_name2 <- "influenza"
```

## Scenario B

Influenza A in `r city_name`

The `r city_name` Pandemic Response committee has gathered the following information for the second meeting of your group. 

You should evaluate the effect(s) of the actions that you took at your last meeting and evaluate the current state of affairs in `r city_name`. 

You should submit 3-5 specific actions for further actions to control the pandemic, using the [workshop 4 pro forma](../proformas/BM424_workshop4_proforma.docx) (also available on MyPlace). You should consider whether you want to continue any of the public health measures you implemented at your previous meeting, or whether you want to stop them; and also whether there are any new, additional actions you would like to take. Submit the pro forma by noon on Friday March 24th, via the submission link on MyPlace. 

## Minutes from the last Pandemic Response Committee Meeting

Actions taken:

1. Extend flu vaccine rollout to farmers (as most common flu strain is H3N2 we are hoping for some cross reactivity with subsequent antibodies to H3N2 because of the same N2) and investigate poultry farms to determine a possible source of the H9N2 strain (which appears to be predominant)

2. Make pharmacists more aware of symptoms and reduce pressure on primary care services and hospitals by activating the national pandemic flu service. Let pharmacies prescribe oseltamivir (antiviral) for  affect people in the age brackets of <5 >65, as these groups are most venerable. 

3. Leaflets sent to offices and posted in NHS buildings/pharmacies and TV/internet adverts. These will encourage mask wearing (N95), getting flu vaccine (if eligible) and to encourage additional flu prevention measures e.g. working from home, if possible, reduce unnecessary travel for people who feel unwell, handwashing and covering coughs and sneezes.


## Pandemic Statistics 

Table 1. Data from the `r city_name` Influenza A outbreak.
<table>
<table border="1">
  <tr>
    <th></th>
    <th>23/02/2024 data</th>
    <th>07/03/2024 data</th>
  </tr>
  <tr>
    <td>Deaths caused by the Influenza A outbreak (total)</td>
    <td>20</td>
    <td>35</td>
  </tr>
  <tr>
    <td>Verified Influenza A cases (total)</td>
    <td>330</td>
    <td>409</td>
  </tr>
  <tr>
    <td>Influenza A hospitalisations (weekly)</td>
    <td>170</td>
    <td>103</td>
  </tr>
    <tr>
    <td>`r hospital_name` ICU bed occupancy (current)</td>
    <td>15</td>
    <td>10</td>
  </tr>
  <tr>
  <td>Number of Influenza A related GP visits (total)</td>
  <td>311</td>
  <td>15</td>
  </tr>
</table>  
<br><br>


## Letters from the Public

```{r emails, echo=FALSE}

clos1 <- c("Yours sincerely,", "Best wishes,", "Kind regards,", "All the best,", "Sincerely,", "Yours truly,", "Respectfully,")
email1 <- c("gldk", "aptr", "bhr", "tgh", "pbr", "js", "lucy", "amd", "oirl", "jim", "ygg", "oli", "end", "lulu", "rye", "att")
adj1 <- c("Disgraceful", "Terrible", "Horrible", "Devastating", "Sad", "Bloody")
emotion1 <- c("outraged", "upset", "extremely vexed", "so angry", "devastated")
sent1 <- c()
wish1 <- c("hope", "hope very much", "wish", "expect", "sincerely hope")
state1 <- c("dreadful state of affairs", "horrible pandemic", "all of the poor people dying", "tragedy")
time1 <- c("immediately", "very soon", "at once", "as soon as possible")
name1 <- c("Anna", "Luke", "Siobhan", "Su", "Ailidh", "Fiona", "Graham", "Madison", "Eleanor", "Rodrigo", "Kieran", "Wilson", "Anika", "Rosemary", "Alise", "Gordon", "Roman", "Karen")
verb1 <- c("devastate", "obliterate", "ruin", "destroy", "crush")
business1 <- c("small coffee shop", "coffee shop", "cafe", "restaurant", "bookshop", "boutique clothing store", "records shop", "used bookstore", "toy store", "sweet shop")
business2 <- c("The Baltyre Shop", "Fraser & Co.", "Bella's", "Around the Corner", "Jewels")
adj2 <- c("nearly", "almost", "virtually", "almost literally", "practically")
conseq1 <- c("lost my business due to those pandemic lockdowns", "had to close because of all the draconian lockdowns", "went out of business", "went bankrupt", "had to shut our doors during COVID")
sent2 <- c()
subj1 <- c()
state2 <- c("awful pandemic", "terrible pandemic", "new crisis", "new pandemic", "new disease")
conseq2 <- c()
sent3 <- c()
sent4 <- c()
subj2 <- c("This Terrible Tragedy", "Another Terrible Loss")
rel1 <- c("my mother-in-law", "my aunt", "my auntie", "my niece", "my nephew", "my husband's best friend", "my wife's best friend", "my sister-in-law", "my brother-in-law", "my uncle", "my granddad", "my gran", "my nana", "my nana's best friend")
sent5 <- c()
sent6 <- c()
```

***

<b>From:</b> `r sample(email1, 1)`_1955@gmail.com <br>
<b>To:</b> PandemicResponseCommittee@`r city_name`.co.uk <br>
<b>Cc:</b>
<b>Subject:</b> This `r sample(adj1, 1)` Pandemic

Dear Pandemic Response Committee

I am `r sample(emotion1, 1)` to hear about your actions tackling the pandemic in `r city_name`. If it isn't enough that the NHS is eroded by decades of underfunding and mismanagement, now you are having pharmacies prescribe medicine. Dire times call for dire measures I know, but surely it is more important that you do something to fix our poor NHS instead of splashing out all this money on useless statues and silly things.

I `r sample(wish1, 1)` that your office is going to do something about this dreadful mess. Pharmacists don't have the proper training to be prescribing drugs and it isn't fair to make them do extra work, either. You'd never think that we live in the 21st century, the state our NHS is in - it's a crying shame.

`r sample(clos1, 1, replace=TRUE)`<br>
`r sample(name1, 1)`

***

<b>From:</b> `r sample(email1, 1)`-88@gmail.com <br>
<b>To:</b> PandemicResponseCommitteet@`r city_name`.co.uk <br>
<b>Cc:</b> city-council@`r city_name`.co.uk <br>
<b>Subject:</b> VACCINES ARE TOXIC

Dear Pandemic Response Committee,

I can already see that you and your office are going to use this new pandemic as yet another excuse for government overreach into citizens' lives. Encouraging mask wearing and vaccination - your hands are already washed in blood. I hope you can sleep at night because I am sure I wouldn't be able to if I were you. How many more innocents need to die before we just STOP it with these TOXIC vaccines?!?!

`r sample(clos1, 1, replace=TRUE)`<br>
`r sample(name1, 1)` 

***


## Newspaper coverage

```{r news, echo=FALSE}

papername1 <- c("News", "Daily Press", "Evening News", "Star", "Telegraph", "Post", "Looking-Glass", "Sentinel", "Times")
authname1 <- c("Maurice", "Cyrus", "Aaron", "Jane", "Abigail", "Ben", "Eden", "Jessica", "Leone", "Louisa", "Louis", "Fred", "Steve", "Barbara", "Norman", "Susan", "Edwin", "Isaac", "Austin", "Hugh", "Roselyne", "Francis", "Frances", "David", "Elliot", "Alan", "Joan", "Lester", "Devendra", "Lettitia", "Clive", "Perry", "J.M.", "S.R.", "A.B.", "Frank", "Mick", "Graham", "Walter", "Tony", "Leana", "Chester", "Peter", "Ward", "Ken", "Alice", "Erin", "Kate", "Niels", "Emma", "Elena", "Mary-Louise", "George", "Omar", "Carol", "Deborah", "Joseph", "Ashleigh", "Emily", "Joyce", "Harry", "Marcus", "Bill", "Martin", "Luis", "Leo", "Byron", "Joseph", "John", "Julia", "Eric", "Thomas", "Pablo", "Lewis", "Willa", "Miguel", "Edith", "Tracy")
surname1 <- c("Chevalier", "Charles", "Chesterton", "Clay", "Cohen", "Collins", "Conway", "Cunningham", "Davis", "Daniels", "Douglas", "Evans", "Elliot", "Fields", "Ford", "Fox", "Gallagher", "Gibson", "Grant", "Harris", "Henry", "Hill", "Holmes", "Hunt", "James", "Jones", "Jensen", "Jennings", "Johnson", "Kay", "Kennedy", "King", "Lamb", "Lane", "Lee", "Lewis", "Locke", "Lynch", "MacArthur", "Mann", "Marin", "Martin", "Matthews", "May", "McCarthy", "McClary", "McGill", "McKay", "Mill", "Miller", "Mitchell", "Moore", "Morris", "Nelson", "Nicoll", "Ogilvy", "Ochs", "O'Brien", "Page", "Patterson", "Perry", "Phillips", "Ray", "Reed", "Rogers", "Russell", "Schiller", "Schultz", "Shelley", "Smith", "Snow", "Spencer", "Stein", "Star", "Stewart", "Stone", "Swift")
pubdate <- c("03/03/2023", "04/03/2023", "05/03/2023", "06/03/2023", "07/03/2023", "08/03/2023", "09/03/2023", "10/03/2023", "11/03/2023", "12/03/2023", "13/03/2023", "14/03/2023", "15/03/2023", "16/03/2023", "17/03/2023")
adj3 <- c("Disgraceful", "Terrible", "Horrible", "Devastating", "Sad", "Bloody")
emotion2 <- c("outraged", "upset", "extremely vexed", "so angry", "devastated")
sent7 <- c()
wish2 <- c("hope", "hope very much", "wish", "expect", "sincerely hope")
state2 <- c("dreadful state of affairs", "horrible pandemic", "all of the poor people dying", "tragedy")
time2 <- c("immediately", "very soon", "at once", "as soon as possible")
name2 <- c("Anna", "Luke", "Siobhan", "Su", "Ailidh", "Fiona", "Graham", "Madison", "Eleanor", "Rodrigo", "Kieran", "Wilson", "Anika", "Rosemary", "Alise", "Gordon", "Roman", "Karen")
verb2 <- c("devastate", "obliterate", "ruin", "destroy", "crush")
adj4 <- c("nearly", "almost", "virtually", "almost literally", "practically")
sent8 <- c()
sent9 <- c()
sent10 <- c()
sent11 <- c()


#set up person details for obits
x <- sample(1:2, 1)
if(x == 1){
pron1 <- "he"
posspron1 <- "his"
obit1name <- sample(c("Charles", "Robert", "Luke", "Phil", "George", "Elijah", "Noah", "William", "Ben", "James", "Henry", "Leo", "Luca", "Ray"), 1)
}
if(x == 2){
pron1 <- "she"
posspron1 <- "her"
obit1name <- sample(c("Dorothy", "Ellen", "Olivia", "Emma", "Charlotte", "Amelia", "Ava", "Sophia", "Millie", "Freya", "Poppy", "Sienna", "Florence"), 1)
}
obit1age <- sample(2:5, 1)
obit1like1 <- sample(c("jigsaw puzzles", "teddy bears", "dinosaurs", "airplanes", "books", "butterflies", "elephants", "hedgehogs", "horses", "fire engines", "penguins", "sail boats", "zebras"), 1)
obit1like2 <- sample(c("giraffes", "koala bears", "dragons", "cars", "movies", "goldfish", "trains", "unicorns", "winter", "trucks", "finger painting", "flowers", "sea turtles"), 1)
obit1siblings <- sample(c("Charlie, Alfie, and Jacob", "Tammy and Beth", "Theodore and Mason", "Rory and Susan", "William and Ethan", "Louise and Edward", "Caleb and Brody", "Carter, David, and Milo", "Billy and Parker", "Livvy and Jane"), 1)
obit1surname <- sample(c("Smith", "Jones", "Williams", "Taylor", "Davies", "Brown", "Wilson", "Evans", "Roberts", "Walker", "Wright", "Thompson", "Hughes", "Edwards", "Green", "Lewis", "Wood", "Martin", "Jackson", "Clark"), 1)


x <- sample(1:3, 1)
if(x == 1){
pron2 <- "he"
posspron2 <- "his"
obit2name <- sample(c("Edward", "Riley", "Hugo", "Ronnie", "Louis", "Grayson", "Caleb", "Benjamin", "Kai", "Jasper", "Albert", "Blake", "Dylan", "Liam"), 1)
}
if(x == 2){
pron2 <- "she"
posspron2 <- "her"
obit2name <- sample(c("Matilda", "Lucy", "Jessica", "Alice", "Maya", "Lottie", "Erin", "Maisie", "Bonnie", "Penelope", "Violet", "Esme", "Aurora"), 1)
}
if(x == 3){
pron2 <- "they"
posspron2 <- "their"
obit2name <- sample(c("Cypress", "Hollis", "Lex", "Landry", "Rory", "Salem", "Sol", "Kit", "Bellamy"), 1)
}

obit2age <- sample(50:90, 1)
obit2prof1 <- sample(c("musician", "author", "comedian", "artist"), 1)
obit2work1 <- sample(c("Green Grass", "A Whole Latte", "Golden Days", "One True Love", "Idle Thoughts", "Hopeless", "Purple Skies", "Framed", "Enemy of Fire", "Friends and Lovers", "My Best Friend", "A Fool's Errand", "Harmful", "Pigeons and Partridges"), 1)
obit2siblings <- sample(c("Luke and Chester", "Emily and Jonathan", "Gloria and Stephen", "Hester and Winifred", "Tammy, Theodore, and Thomas", "Frank and Thelma", "Eva and Elaine", "Charlotte and Harper", "Daisy and Phoebe", "Jim, Ella, and Evie"), 1)
obit2surname <- sample(c("Smith", "Jones", "Williams", "Taylor", "Davies", "Brown", "Wilson", "Evans", "Roberts", "Walker", "Wright", "Thompson", "Hughes", "Edwards", "Green", "Lewis", "Wood", "Martin", "Jackson", "Clark", "Campbell", "Burns", "Murphy", "Watt", "Marshall", "White", "Stevenson", "Young", "Watson", "Morrison", "King", "Bruce", "Hill", "Gibson", "Gordon"), 1)

```

<font size="+3"><b>`r city_name` `r sample(papername1, 1)`</b></font><br>
<font size="+2"><b>`r city_name` says farewell to pandemic's youngest victim</b></font><br>
by `r sample(authname1, 1)` `r sample(surname1, 1)`
`r sample(pubdate, 1)`

The `r dis_name2` pandemic ravaging `r city_name` has claimed yet another victim. There have been 35 deaths in the pandemic so far, but perhaps the most tragic loss is `r obit1name` `r obit1surname` - at only `r obit1age`, the youngest victim that the pandemic has claimed.    

`r obit1name` `r obit1surname` liked `r obit1like1` and `r obit1like2`. Friends and family say that `r pron1` was always `r sample(c("a delight", "an absolute joy", "a treasure", "the most precious child"), 1)`. 

`r obit1name` is survived by `r posspron1` parents and grandparents, and by `r posspron1` siblings `r obit1siblings`. 

The funeral service will be held `r sample(c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday"), 1)` at `r sample(c("St. Ninian's", "Trinity Baptist Church", "Westlake Memorial", "St. Elfrida's Catholic Church", "St. Mary's", "Trinity Church", "St. Andrew's", "St. Judes"), 1)`.

***

<font size="+3"><b>`r city_name` `r sample(papername1, 1)`</b></font><br>
<font size="+2"><b>`r city_name` says farewell to local legend</b></font><br>
by `r sample(authname1, 1)` `r sample(surname1, 1)`
`r sample(pubdate, 1)`

The `r dis_name2` pandemic ravaging `r city_name` has claimed yet another victim. `r obit2name` `r obit2surname`, local `r obit2prof1` and star, sadly passed away on `r sample(c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday"), 1)`. 

`r obit2name` was perhaps best known for `r posspron2` `r sample(2000:2015, 1)` work `r obit2work1` , but fans say that the rest of `r posspron2` work was equally as `r sample(c("memorable", "genre-changing", "excellent", "influential"), 1)`. 

`r obit2name` is survived by `r posspron2` `r sample(c("partner", "husband", "wife"), 1)`, and by `r posspron2` siblings `r obit2siblings`. 

The funeral service will be held `r sample(c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday"), 1)` at `r sample(c("St. Ninian's", "Trinity Baptist Church", "Westlake Memorial", "St. Elfrida's Catholic Church", "St. Mary's", "Trinity Church", "St. Andrew's", "St. Judes"), 1)`.

***

<font size="+3"><b>`r city_name` `r sample(papername1, 1)`</b></font><br>
<font size="+2"><b>`r city_name` pandemic council making great strides</b></font><br>
by `r sample(authname1, 1)` `r sample(surname1, 1)`
`r sample(pubdate, 1)`

Citizens of `r city_name` should be `r sample(c("grateful", "thankful", "glad"), 1)` that the city's Pandemic Response Council, `r sample(c("swiftly", "quickly", "hurriedly"), 1)` convened when a new pandemic began to hit `r city_name`, has been so effective. While the initial death toll from the pandemic appeared to be quite `r sample(c("alarming", "devastating", "serious", "high", "heavy"), 1)`, the actions taken by the PRC seem to have been most effective. 

Officials from `r sample(c("the NHS", "Public Health Scotland", "the World Health Organisation", "the Center for Disease Control", "the Red Cross"), 1)` have publicly praised the `r city_name` PRC, saying that `r sample(c("it is difficult to imagine a more effective public health response", "their actions have been extremely effective", "the PRC has done all of the right things", "this is a triumph that shows how effective public health responses can be", "countless lives have been saved due to the actions of the PRC"), 1)`

There have been 5 deaths due to `r dis_name2` in `r city_name` this week. This is an enormous decrease, and hopefully `r city_name` will see the death toll continue to decrease in the coming weeks. 

***

<font size="+3"><b>`r city_name` `r sample(papername1, 1)`</b></font><br>
<font size="+2"><b>Yet more overreach in the name of "science"</b></font><br>
by `r sample(authname1, 1)` `r sample(surname1, 1)`
`r sample(pubdate, 1)`

Governments across the globe have seen how successful power-grabs in the name of public health can be, following on the wave of restrictions imposed because of so-called viral diseases like COVID-19 and "mpox". So-called scientists are fearmongering - aerosols, monkeys, "bird" flu - now they think that they can fool us into thinking that the very air we breathe is unsafe. Citizens of `r city_name` should stand strong against this terrible tyranny! No more mask mandates, no more senseless restrictions!

Our elders should not be left to die alone, left frightened and hopeless in a mandatory lockdown claimed to be "for their benefit." Our children should not be left to struggle through "pandemic" after "pandemic" - their language and literacy skills have been left behind due to these lockdowns, and their mental health is suffering. It is time that we take back control of our lives and end this tyranny of fear-mongering and so-called science. Citizens of `r city_name`, stand with me and resist this most recent attack on your freedoms and your lives. 

*** 

<font size="+3"><b>`r sample(c("BBC Scotland", "The Guardian", "The Independent"), 1)` </b></font><br>
<font size="+2"><b>`r dis_name2` pandemic in `r city_name`</b></font><br>
by `r sample(authname1, 1)` `r sample(surname1, 1)`
`r sample(pubdate, 1)`

Hard on the heels of the COVID-19 pandemic and a number of other health scares (monkeypox, or "mpox", Strep A, and worries about other infectious disease outbreaks), another pandemic has hit the Scottish town of `r city_name`. This time, it's `r dis_name2` - the same virus that has caused global pandemics in the past.

There have been 35 deaths in the pandemic so far, but perhaps the most frightening aspect to this new pandemic is rumours that this variant of avian influenza has crossed the species barrier and can be transmitted from human to human.

Scientists have been talking about this possibility for years, warning of the potential for a massive pandemic similar to the 1918 "Spanish Flu".

Is the virus circulating in `r city_name` the one, or is the next influenza pandemic still around the corner?


## Data gathered by the committee since the previous meeting

### RT-PCR testing for influenza virus

Table 2. RT-PCR testing of poultry farms in the `r city_name` `r dis_name2` outbreak.
<table>
<table border="1">
  <tr>
    <th>Location</th>
    <th>Number of animals tested</th>
    <th>Number of positive RT-PCR tests</th>
  </tr>
  <tr>
    <td>Sue's Duck Farm</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:10, 1)`</td>
  </tr>
  <tr>
    <td>Craig's Chickens</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:10, 1)`</td>
  </tr>
  <tr>
    <td>Ellenmere Farm</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:10, 1)`</td>
  </tr>
  <tr>
    <td>Highgrove</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:10, 1)`</td>
  </tr>
  <tr>
    <td>Clucks-alot Farms</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:10, 1)`</td>
  </tr>
  <tr>
    <td>Lucky Clucky Farms</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:10, 1)`</td>
  </tr>
  <tr>
    <td>The Golden Goose</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:10, 1)`</td>
  </tr>
  <tr>
    <td>Hightree Nature Reserve</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:10, 1)`</td>
  </tr>
  <tr>
    <td>Lakesmere</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:10, 1)`</td>
  </tr>
  <tr>
    <td>Heather and Gorse Farms</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:10, 1)`</td>
  </tr>
  <tr>
    <td>Grace's Ganders</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:10, 1)`</td>
  </tr>
  <tr>
    <td>Loosey Goosey Farms</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:10, 1)`</td>
  </tr>
  <tr>
    <td>The Chicken Run</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:10, 1)`</td>
  </tr>
  <tr>
    <td>Greenacres</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:10, 1)`</td>
  </tr>
  <tr>
    <td>Hill Farm</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:10, 1)`</td>
  </tr>
  <tr>
    <td>Loyola's Turkey Farm</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:10, 1)`</td>
  </tr>
  <tr>
    <td>The Balltyre Quail Farm</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:10, 1)`</td>
  </tr>
  <tr>
    <td>Goosopolis Farms</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:10, 1)`</td>
  </tr>
  <tr>
    <td>Cordelia and Ken's Chickens</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:10, 1)`</td>
  </tr>
  <tr>
    <td>Fair Hope Farm</td>
    <td>`r sample(30:100, 1)`</td>
    <td>`r sample(0:10, 1)`</td>
  </tr>
</table>  
<br><br>

