---
title: 'BM424 workshop: infectious disease outbreak control'
author: "Morgan Feeney"
date: "17/03/2023"
output: 
  bookdown::html_document2:
    toc: true
    toc_float:
      toc_collapsed: false
    number_sections: false 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(knitr)


city_name <- "Malleith" ##replace all instances of "Malleith" with new scenario name
hospital_name <- "Central Highland" ##replace all instances of "Central Highland" with new scenario name
dis_name3 <- "MRSA"
outbreak_deaths <- 10 + 8 + 6

```

## Scenario C: MRSA in `r city_name`

The `r city_name` Pandemic Response committee has gathered the following information for the second meeting of your group. 

You should evaluate the effect(s) of the actions that you took at your last meeting and evaluate the current state of affairs in `r city_name`. 

You should submit 3-5 specific actions for further actions to control the pandemic, using the [workshop 4 pro forma](../proformas/BM424_workshop4_proforma.docx) (also available on MyPlace). You should consider whether you want to continue any of the public health measures you implemented at your previous meeting, or whether you want to stop them; and also whether there are any new, additional actions you would like to take. Submit the pro forma by noon on Friday March 24th, via the submission link on MyPlace. 

## Minutes from the last Pandemic Response Committee Meeting

Actions taken:

1. Advertise how MRSA is spread (which is through contact of an infected person or item) and how to reduce spread through hygiene and no sharing of towels and razors.
Do this advertisement through radio, tv adverts and posters.

2. Train hospital and clinic staff in the Central Highland hospital in how to reduce spread of MRSA via washing hands before and after seeing patients and covering wounds or cuts they may have. And train them on how to decontaminate MRSA infected patients via antiseptic wash for skin and nose. And train them to not share infected medical items like thermometers and sphygmomanometer (to measure blood pressure)

3. Isolate infected patients to reduce transmission to healthy patients

4. Screen hospital staff for MRSA infection via swab from nose. Test swab on denim blue agar:
positive= growth of denim blue colonies
Negative= inhibition or growth of white colonies
CONTACT IN TRACING

5. Order vancomycin to treat MRSA.
Only use in severe MRSA patients to prevent resistance of MRSA towards vancomycin

## Pandemic Statistics 

Table 1. Data from the `r city_name` MRSA outbreak.
<table>
<table border="1">
  <tr>
    <th></th>
    <th>23/02/2024 data</th>
    <th>07/03/2024 data</th>
  </tr>
  <tr>
    <td>Deaths caused by the MRSA outbreak (total)</td>
    <td>10</td>
    <td>24</td>
  </tr>
  <tr>
    <td>Verified MRSA cases (total)</td>
    <td>140</td>
    <td>250</td>
  </tr>
  <tr>
    <td>MRSA hospitalisations (weekly)</td>
    <td>145</td>
    <td>98</td>
  </tr>
    <tr>
    <td>`r hospital_name` ICU bed occupancy (current)</td>
    <td>15</td>
    <td>4</td>
  </tr>
  <tr>
  <td>Number of MRSA related GP visits (total)</td>
  <td>73</td>
  <td>45</td>
  </tr>
</table>  
<br><br>


## Letters from the Public

```{r emails, echo=FALSE}

clos1 <- c("Yours sincerely,", "Best wishes,", "Kind regards,", "All the best,", "Sincerely,", "Yours truly,", "Respectfully,")
email1 <- c("gldk", "aptr", "bhr", "tgh", "pbr", "js", "lucy", "amd", "oirl", "jim", "ygg", "oli", "end", "lulu", "rye", "att")
adj1 <- c("Disgraceful", "Terrible", "Horrible", "Devastating", "Sad", "Bloody")
emotion1 <- c("outraged", "upset", "extremely vexed", "so angry", "devastated")
sent1 <- c()
wish1 <- c("hope", "hope very much", "wish", "expect", "sincerely hope")
state1 <- c("dreadful state of affairs", "horrible pandemic", "all of the poor people dying", "tragedy")
time1 <- c("immediately", "very soon", "at once", "as soon as possible")
name1 <- c("Anna", "Luke", "Siobhan", "Su", "Ailidh", "Fiona", "Graham", "Madison", "Eleanor", "Rodrigo", "Kieran", "Wilson", "Anika", "Rosemary", "Alise", "Gordon", "Roman", "Karen")
verb1 <- c("devastate", "obliterate", "ruin", "destroy", "crush")
business1 <- c("small coffee shop", "coffee shop", "cafe", "restaurant", "bookshop", "boutique clothing store", "records shop", "used bookstore", "toy store", "sweet shop")
business2 <- c("The Baltyre Shop", "Fraser & Co.", "Bella's", "Around the Corner", "Jewels")
adj2 <- c("nearly", "almost", "virtually", "almost literally", "practically")
conseq1 <- c("lost my business due to those pandemic lockdowns", "had to close because of all the draconian lockdowns", "went out of business", "went bankrupt", "had to shut our doors during COVID")
sent2 <- c()
subj1 <- c()
state2 <- c("awful pandemic", "terrible pandemic", "new crisis", "new pandemic", "new disease")
conseq2 <- c()
sent3 <- c()
sent4 <- c()
subj2 <- c("This Terrible Tragedy", "Another Terrible Loss")
rel1 <- c("my mother-in-law", "my aunt", "my auntie", "my niece", "my nephew", "my husband's best friend", "my wife's best friend", "my sister-in-law", "my brother-in-law", "my uncle", "my granddad", "my gran", "my nana", "my nana's best friend")
sent5 <- c()
sent6 <- c()
```

***

<b>From:</b> `r sample(email1, 1)`_1955@gmail.com <br>
<b>To:</b> PandemicResponseCommittee@`r city_name`.co.uk <br>
<b>Cc:</b>
<b>Subject:</b> This `r sample(adj1, 1)` Pandemic

Dear Pandemic Response Committee

I am so frightened by the current pandemic that is rampaging through my beloved city. I have never heard of this MRSA before but it is dreadfully scary. The radio advert I heard yesterday made it sound like a huge problem. What is the world coming to, I ask you, with the MRSA plague on top of the COVID19 one already and the monkeypox as well. It feels like a judgement on our times.

Thank you so much for your hard work keeping us safe, I heard that you were buying in some vancomycin to kill these evil superbugs. I think you should distribute this to everyone in Malleith so that we can be safe from thi sterror.

`r sample(clos1, 1, replace=TRUE)`<br>
`r sample(name1, 1)`

***

<b>From:</b> `r sample(email1, 1)`-88@gmail.com <br>
<b>To:</b> PandemicResponseCommitteet@`r city_name`.co.uk <br>
<b>Cc:</b> city-council@`r city_name`.co.uk <br>
<b>Subject:</b> The state of our hospitals

Dear Pandemic Response Committee,

I am so worried about my nan, who is going into the hospital for a hip replacement surgery this coming Sunday. She really needs it as the cartilage in her joints is completely gone and so it is very painful for her to walk. 

I am really worried that she will have caught the MRSA from the hospital and will die. I heard from Nell who is a nurse there that they have new training measures in place to try to prevent the spread of the superbug, but I am just so worried that it will not be enough. Are there any further measures that you can take to help to keep us all safe?

I know the NHS is struggling because it has been underfunded for so many years, but if you can find a little bit of extra money somewhere, I am sure it would make a real difference to my nan.


Thank you so much for all the hard work you do,<br>
`r sample(name1, 1)` 

***

## News Coverage of the `r city_name` MRSA outbreak


```{r news, echo=FALSE}

papername1 <- c("News", "Daily Press", "Evening News", "Star", "Telegraph", "Post", "Looking-Glass", "Sentinel", "Times")
authname1 <- c("Maurice", "Cyrus", "Aaron", "Jane", "Abigail", "Ben", "Eden", "Jessica", "Leone", "Louisa", "Louis", "Fred", "Steve", "Barbara", "Norman", "Susan", "Edwin", "Isaac", "Austin", "Hugh", "Roselyne", "Francis", "Frances", "David", "Elliot", "Alan", "Joan", "Lester", "Devendra", "Lettitia", "Clive", "Perry", "J.M.", "S.R.", "A.B.", "Frank", "Mick", "Graham", "Walter", "Tony", "Leana", "Chester", "Peter", "Ward", "Ken", "Alice", "Erin", "Kate", "Niels", "Emma", "Elena", "Mary-Louise", "George", "Omar", "Carol", "Deborah", "Joseph", "Ashleigh", "Emily", "Joyce", "Harry", "Marcus", "Bill", "Martin", "Luis", "Leo", "Byron", "Joseph", "John", "Julia", "Eric", "Thomas", "Pablo", "Lewis", "Willa", "Miguel", "Edith", "Tracy")
surname1 <- c("Chevalier", "Charles", "Chesterton", "Clay", "Cohen", "Collins", "Conway", "Cunningham", "Davis", "Daniels", "Douglas", "Evans", "Elliot", "Fields", "Ford", "Fox", "Gallagher", "Gibson", "Grant", "Harris", "Henry", "Hill", "Holmes", "Hunt", "James", "Jones", "Jensen", "Jennings", "Johnson", "Kay", "Kennedy", "King", "Lamb", "Lane", "Lee", "Lewis", "Locke", "Lynch", "MacArthur", "Mann", "Marin", "Martin", "Matthews", "May", "McCarthy", "McClary", "McGill", "McKay", "Mill", "Miller", "Mitchell", "Moore", "Morris", "Nelson", "Nicoll", "Ogilvy", "Ochs", "O'Brien", "Page", "Patterson", "Perry", "Phillips", "Ray", "Reed", "Rogers", "Russell", "Schiller", "Schultz", "Shelley", "Smith", "Snow", "Spencer", "Stein", "Star", "Stewart", "Stone", "Swift")
pubdate <- c("03/03/2023", "04/03/2023", "05/03/2023", "06/03/2023", "07/03/2023", "08/03/2023", "09/03/2023", "10/03/2023", "11/03/2023", "12/03/2023", "13/03/2023", "14/03/2023", "15/03/2023", "16/03/2023", "17/03/2023")
adj3 <- c("Disgraceful", "Terrible", "Horrible", "Devastating", "Sad", "Bloody")
emotion2 <- c("outraged", "upset", "extremely vexed", "so angry", "devastated")
sent7 <- c()
wish2 <- c("hope", "hope very much", "wish", "expect", "sincerely hope")
state2 <- c("dreadful state of affairs", "horrible pandemic", "all of the poor people dying", "tragedy")
time2 <- c("immediately", "very soon", "at once", "as soon as possible")
name2 <- c("Anna", "Luke", "Siobhan", "Su", "Ailidh", "Fiona", "Graham", "Madison", "Eleanor", "Rodrigo", "Kieran", "Wilson", "Anika", "Rosemary", "Alise", "Gordon", "Roman", "Karen")
verb2 <- c("devastate", "obliterate", "ruin", "destroy", "crush")
adj4 <- c("nearly", "almost", "virtually", "almost literally", "practically")
sent8 <- c()
sent9 <- c()
sent10 <- c()
sent11 <- c()


#set up person details for obits
x <- sample(1:2, 1)
if(x == 1){
pron1 <- "he"
posspron1 <- "his"
obit1name <- sample(c("Charles", "Robert", "Luke", "Phil", "George", "Elijah", "Noah", "William", "Ben", "James", "Henry", "Leo", "Luca", "Ray"), 1)
}
if(x == 2){
pron1 <- "she"
posspron1 <- "her"
obit1name <- sample(c("Dorothy", "Ellen", "Olivia", "Emma", "Charlotte", "Amelia", "Ava", "Sophia", "Millie", "Freya", "Poppy", "Sienna", "Florence"), 1)
}
obit1age <- sample(2:5, 1)
obit1like1 <- sample(c("jigsaw puzzles", "teddy bears", "dinosaurs", "airplanes", "books", "butterflies", "elephants", "hedgehogs", "horses", "fire engines", "penguins", "sail boats", "zebras"), 1)
obit1like2 <- sample(c("giraffes", "koala bears", "dragons", "cars", "movies", "goldfish", "trains", "unicorns", "winter", "trucks", "finger painting", "flowers", "sea turtles"), 1)
obit1siblings <- sample(c("Charlie, Alfie, and Jacob", "Tammy and Beth", "Theodore and Mason", "Rory and Susan", "William and Ethan", "Louise and Edward", "Caleb and Brody", "Carter, David, and Milo", "Billy and Parker", "Livvy and Jane"), 1)
obit1surname <- sample(c("Smith", "Jones", "Williams", "Taylor", "Davies", "Brown", "Wilson", "Evans", "Roberts", "Walker", "Wright", "Thompson", "Hughes", "Edwards", "Green", "Lewis", "Wood", "Martin", "Jackson", "Clark"), 1)


x <- sample(1:3, 1)
if(x == 1){
pron2 <- "he"
posspron2 <- "his"
obit2name <- sample(c("Edward", "Riley", "Hugo", "Ronnie", "Louis", "Grayson", "Caleb", "Benjamin", "Kai", "Jasper", "Albert", "Blake", "Dylan", "Liam"), 1)
}
if(x == 2){
pron2 <- "she"
posspron2 <- "her"
obit2name <- sample(c("Matilda", "Lucy", "Jessica", "Alice", "Maya", "Lottie", "Erin", "Maisie", "Bonnie", "Penelope", "Violet", "Esme", "Aurora"), 1)
}
if(x == 3){
pron2 <- "they"
posspron2 <- "their"
obit2name <- sample(c("Cypress", "Hollis", "Lex", "Landry", "Rory", "Salem", "Sol", "Kit", "Bellamy"), 1)
}

obit2age <- sample(50:90, 1)
obit2prof1 <- sample(c("musician", "author", "comedian", "artist"), 1)
obit2work1 <- sample(c("Green Grass", "A Whole Latte", "Golden Days", "One True Love", "Idle Thoughts", "Hopeless", "Purple Skies", "Framed", "Enemy of Fire", "Friends and Lovers", "My Best Friend", "A Fool's Errand", "Harmful", "Pigeons and Partridges"), 1)
obit2siblings <- sample(c("Luke and Chester", "Emily and Jonathan", "Gloria and Stephen", "Hester and Winifred", "Tammy, Theodore, and Thomas", "Frank and Thelma", "Eva and Elaine", "Charlotte and Harper", "Daisy and Phoebe", "Jim, Ella, and Evie"), 1)
obit2surname <- sample(c("Smith", "Jones", "Williams", "Taylor", "Davies", "Brown", "Wilson", "Evans", "Roberts", "Walker", "Wright", "Thompson", "Hughes", "Edwards", "Green", "Lewis", "Wood", "Martin", "Jackson", "Clark", "Campbell", "Burns", "Murphy", "Watt", "Marshall", "White", "Stevenson", "Young", "Watson", "Morrison", "King", "Bruce", "Hill", "Gibson", "Gordon"), 1)

```


<font size="+3"><b>`r city_name` `r sample(papername1, 1)`</b></font><br>
<font size="+2"><b>`r city_name` says farewell to pandemic's youngest victim</b></font><br>
by `r sample(authname1, 1)` `r sample(surname1, 1)`
`r sample(pubdate, 1)`

The `r dis_name3` pandemic ravaging `r city_name` has claimed yet another victim. There have been `r outbreak_deaths` deaths in the pandemic so far, but perhaps the most tragic loss is `r obit1name` `r obit1surname` - at only `r obit1age`, the youngest victim that the pandemic has claimed.    

`r obit1name` `r obit1surname` liked `r obit1like1` and `r obit1like2`. Friends and family say that `r pron1` was always `r sample(c("a delight", "an absolute joy", "a treasure", "the most precious child"), 1)`. 

`r obit1name` is survived by `r posspron1` parents and grandparents, and by `r posspron1` siblings `r obit1siblings`. 

The funeral service will be held `r sample(c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday"), 1)` at `r sample(c("St. Ninian's", "Trinity Baptist Church", "Westlake Memorial", "St. Elfrida's Catholic Church", "St. Mary's", "Trinity Church", "St. Andrew's", "St. Judes"), 1)`.

***

<font size="+3"><b>`r city_name` `r sample(papername1, 1)`</b></font><br>
<font size="+2"><b>`r city_name` says farewell to local legend</b></font><br>
by `r sample(authname1, 1)` `r sample(surname1, 1)`
`r sample(pubdate, 1)`

The `r dis_name3` pandemic ravaging `r city_name` has claimed yet another victim. `r obit2name` `r obit2surname`, local `r obit2prof1` and star, sadly passed away on `r sample(c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday"), 1)`. 

`r obit2name` was perhaps best known for `r posspron2` `r sample(2000:2015, 1)` work `r obit2work1` , but fans say that the rest of `r posspron2` work was equally as `r sample(c("memorable", "genre-changing", "excellent", "influential"), 1)`. 

`r obit2name` is survived by `r posspron2` `r sample(c("partner", "husband", "wife"), 1)`, and by `r posspron2` siblings `r obit2siblings`. 

The funeral service will be held `r sample(c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday"), 1)` at `r sample(c("St. Ninian's", "Trinity Baptist Church", "Westlake Memorial", "St. Elfrida's Catholic Church", "St. Mary's", "Trinity Church", "St. Andrew's", "St. Judes"), 1)`.

***

<font size="+3"><b>`r city_name` `r sample(papername1, 1)`</b></font><br>
<font size="+2"><b>`r city_name` pandemic council making great strides</b></font><br>
by `r sample(authname1, 1)` `r sample(surname1, 1)`
`r sample(pubdate, 1)`

Citizens of `r city_name` should be `r sample(c("grateful", "thankful", "glad"), 1)` that the city's Pandemic Response Council, `r sample(c("swiftly", "quickly", "hurriedly"), 1)` convened when a new pandemic began to hit `r city_name`, has been so effective. While the initial death toll from the pandemic appeared to be quite `r sample(c("alarming", "devastating", "serious", "high", "heavy"), 1)`, the actions taken by the PRC seem to have been most effective. 

Officials from `r sample(c("the NHS", "Public Health Scotland", "the World Health Organisation", "the Center for Disease Control", "the Red Cross"), 1)` have publicly praised the `r city_name` PRC, saying that `r sample(c("it is difficult to imagine a more effective public health response", "their actions have been extremely effective", "the PRC has done all of the right things", "this is a triumph that shows how effective public health responses can be", "countless lives have been saved due to the actions of the PRC"), 1)`

There have been 6 deaths due to `r dis_name3` in `r city_name` this week. This is an enormous decrease, and hopefully `r city_name` will see the death toll continue to decrease in the coming weeks. 

***

<font size="+3"><b>`r city_name` `r sample(papername1, 1)`</b></font><br>
<font size="+2"><b>Yet more overreach in the name of "science"</b></font><br>
by `r sample(authname1, 1)` `r sample(surname1, 1)`
`r sample(pubdate, 1)`

Governments across the globe have seen how successful power-grabs in the name of public health can be, following on the wave of restrictions imposed because of so-called viral diseases like COVID-19 and "mpox". So-called scientists are fearmongering - aerosols, monkeys, "bird" flu - now they think that they can fool us into thinking that the air and water are unsafe. Citizens of `r city_name` should stand strong against this terrible tyranny! No more mask mandates, no more senseless restrictions!

Our elders should not be left to die alone, left frightened and hopeless in a mandatory lockdown claimed to be "for their benefit." Our children should not be left to struggle through "pandemic" after "pandemic" - their language and literacy skills have been left behind due to these lockdowns, and their mental health is suffering. It is time that we take back control of our lives and end this tyranny of fear-mongering and so-called science. Citizens of `r city_name`, stand with me and resist this most recent attack on your freedoms and your lives. 

*** 

<font size="+3"><b>`r sample(c("BBC Scotland", "The Guardian", "The Independent"), 1)` </b></font><br>
<font size="+2"><b>`r dis_name3` pandemic in `r city_name`</b></font><br>
by `r sample(authname1, 1)` `r sample(surname1, 1)`
`r sample(pubdate, 1)`

Hard on the heels of the COVID-19 pandemic and a number of other health scares (monkeypox, or "mpox", avian flu, and worries about other infectious disease outbreaks), another pandemic has hit the Scottish town of `r city_name`. This time, it's MRSA, a bacterium that is resistant to the antibiotic methicillin

There have been `r outbreak_deaths` deaths in the pandemic so far, but perhaps the most frightening aspect to this new pandemic is rumours that these MRSA strains may have become resistant to even more antibiotics - a truly chilling possibility.

Scientists have been warning about the antibiotic resistance crisis for years, saying that careless use of antibiotics could mean that these precious medicines will no longer be available to us in the future. 

Some of the MRSA strains found in `r city_name` are reportedly resistant to all clinically available antibiotics, and scientists warn that these drug-resistant pathogens might be able to spread to new locations. Will nearby towns be next, or could these MRSA strains go as global as the SARS-COV2 virus did?

***
## Data gathered

## Microbiological Investigation of the `r city_name` `r dis_name3` outbreak

Swab samples were plated on Mannitol Salt Agar (MSA) +/- oxacillin

Table 2. Microbiological testing of patients and homes in the `r city_name` `r dis_name3` outbreak.
<table>
<table border="1">
  <tr>
    <th>Hospital Staff # (Names Redacted)</th>
    <th>Number of colonies on Denim Blue Agar
    (colour)</th>
  </tr>
  <tr>
    <td># 1</td>
    <td>`r sample(30:100, 1)`, `r sample(c("white", "white", "white", "white", "blue"), 1)`</td>
  </tr>
  <tr>
    <td># 2</td>
    <td>`r sample(30:100, 1)`, `r sample(c("white", "white", "white", "white", "blue"), 1)`</td>
  </tr>
  <tr>
    <td># 3</td>
    <td>0</td>
  </tr>
  <tr>
    <td># 4</td>
    <td>0</td>
  </tr>
  <tr>
    <td># 5</td>
    <td>0</td>
  </tr>
  <tr>
    <td># 6</td>
    <td>0</td>
  </tr>
  <tr>
    <td># 7</td>
    <td>`r sample(30:100, 1)`, `r sample(c("white", "white", "white", "white", "blue"), 1)`</td>
  </tr>
  <tr>
    <td># 8</td>
    <td>0</td>
  </tr>
  <tr>
    <td># 9</td>
    <td>0</td>
  </tr>
  <tr>
    <td># 10</td>
    <td>0</td>
  </tr>
  <tr>
    <td># 11</td>
    <td>`r sample(30:100, 1)`, `r sample(c("white", "white", "white", "white", "blue"), 1)`</td>
  </tr>
  <tr>
    <td># 12</td>
    <td>0</td>
  </tr>
  <tr>
    <td># 13</td>
    <td>0</td>
  </tr>
  <tr>
    <td># 14</td>
    <td>`r sample(30:100, 1)`, `r sample(c("white", "white", "white", "white", "blue"), 1)`</td>
  </tr>
  <tr>
    <td># 15</td>
    <td>0</td>
  </tr>
  <tr>
    <td># 16</td>
    <td>0</td>
  </tr>
  <tr>
    <td># 17</td>
    <td>0</td>
  </tr>
  <tr>
    <td># 18</td>
    <td>0</td>
  </tr>
  <tr>
    <td># 19</td>
    <td>0</td>
  </tr>
  <tr>
    <td># 20</td>
    <td>0</td>
  </tr>
  <tr>
    <td># 21</td>
    <td>0</td>
  </tr>
  <tr>
    <td># 22</td>
    <td>0</td>
  </tr>
    <tr>
    <td># 23</td>
    <td>0</td>
  </tr>
    <tr>
    <td># 24</td>
    <td>0</td>
  </tr>
    <tr>
    <td># 25</td>
    <td>0</td>
  </tr>
    <tr>
    <td># 26</td>
    <td>`r sample(30:100, 1)`, `r sample(c("white", "white", "white", "white", "blue"), 1)`</td>
  </tr>
    <tr>
    <td># 27</td>
    <td>0</td>
  </tr>
    <tr>
    <td># 28</td>
    <td>0</td>
  </tr>
    <tr>
    <td># 29</td>
    <td>0</td>
  </tr>
    <tr>
    <td># 30</td>
    <td>0</td>
  </tr>
</table>  
<br><br>
