---
title: 'BM424 workshop: infectious disease outbreak control'
author: "Morgan Feeney"
date: "17/03/2023"
output: 
  bookdown::html_document2:
    toc: true
    toc_float:
      toc_collapsed: false
    number_sections: false 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(knitr)


city_name <- "Inverkeld" 
hospital_name <- "Queen Rose" 
```

## Scenario A

<i>Legionella</i> in `r city_name`

The `r city_name` Pandemic Response committee has gathered the following information for the second meeting of your group. 

You should evaluate the effect(s) of the actions that you took at your last meeting and evaluate the current state of affairs in `r city_name`. 

You should submit 3-5 specific actions for further actions to control the pandemic, using the [workshop 4 pro forma](../proformas/BM424_workshop4_proforma.docx) (also available on MyPlace). You should consider whether you want to continue any of the public health measures you implemented at your previous meeting, or whether you want to stop them; and also whether there are any new, additional actions you would like to take. Submit the pro forma by noon on Friday March 24th, via the submission link on MyPlace. 

## Minutes from the last Pandemic Response Committee Meeting

Actions taken:
1. Keep in contact with governmental organisations, health authorities and the local community about pandemic strategies to control and prevent the spread of the pathogen.
2. Provide adequate training/education on the appropriate use of PPE as well as where to access it. Plus, stock up on PPE (hospital preparedness).
3. Communicate with hospital staff, patients and the local community to provide information on the pandemic and updated hospital policies to ensure hospital preparedness.
4. Devise plans to increase the hospital’s capacity to accommodate a surge of patients (e.g., set up additional treatment areas in the hospital and consider collaborating with healthcare professionals from other institutions).
5. Implement surveillance technology to keep record of critical care capacity.


## Pandemic Statistics 

Table 1. Data from the `r city_name` <i>Legionella</i> outbreak.
<table>
<table border="1">
  <tr>
    <th></th>
    <th>23/02/2024 data</th>
    <th>07/03/2024 data</th>
  </tr>
  <tr>
    <td>Deaths caused by the <i>Legionella</i> outbreak</td>
    <td>23</td>
    <td></td>
  </tr>
  <tr>
    <td>Verified <i>Legionella</i> cases</td>
    <td></td>
    <td></td>
  </tr>
  <tr>
    <td><i>Legionella</i> hospitalisations</td>
    <td>54</td>
    <td></td>
  </tr>
    <tr>
    <td>`r hospital_name` ICU bed occupancy</td>
    <td>13</td>
    <td></td>
  </tr>
  <tr>
  <td>Number of <i>Legionella</i> related GP visits (total)</td>
  <td></td>
  <td></td>
  </tr>
</table>  
<br><br>


## Letters from the Public

```{r emails, echo=FALSE}

clos1 <- c("Yours sincerely,", "Best wishes,", "Kind regards,", "All the best,", "Sincerely,", "Yours truly,", "Respectfully,")
email1 <- c("gldk", "aptr", "bhr", "tgh", "pbr", "js", "lucy", "amd", "oirl", "jim", "ygg", "oli", "end", "lulu", "rye", "att")
adj1 <- c("Disgraceful", "Terrible", "Horrible", "Devastating", "Sad", "Bloody")
emotion1 <- c("outraged", "upset", "extremely vexed", "so angry", "devastated")
sent1 <- c()
wish1 <- c("hope", "hope very much", "wish", "expect", "sincerely hope")
state1 <- c("dreadful state of affairs", "horrible pandemic", "all of the poor people dying", "tragedy")
time1 <- c("immediately", "very soon", "at once", "as soon as possible")
name1 <- c("Anna", "Luke", "Siobhan", "Su", "Ailidh", "Fiona", "Graham", "Madison", "Eleanor", "Rodrigo", "Kieran", "Wilson", "Anika", "Rosemary", "Alise", "Gordon", "Roman", "Karen")
verb1 <- c("devastate", "obliterate", "ruin", "destroy", "crush")
business1 <- c("small coffee shop", "coffee shop", "cafe", "restaurant", "bookshop", "boutique clothing store", "records shop", "used bookstore", "toy store", "sweet shop")
business2 <- c("The Inverkeld Shop", "Fraser & Co.", "Bella's", "Around the Corner", "Jewels")
adj2 <- c("nearly", "almost", "virtually", "almost literally", "practically")
conseq1 <- c("lost my business due to those pandemic lockdowns", "had to close because of all the draconian lockdowns", "went out of business", "went bankrupt", "had to shut our doors during COVID")
sent2 <- c()
subj1 <- c()
state2 <- c("awful pandemic", "terrible pandemic", "new crisis", "new pandemic", "new disease")
conseq2 <- c()
sent3 <- c()
sent4 <- c()
subj2 <- c("This Terrible Tragedy", "Another Terrible Loss")
rel1 <- c("my mother-in-law", "my aunt", "my auntie", "my niece", "my nephew", "my husband's best friend", "my wife's best friend", "my sister-in-law", "my brother-in-law", "my uncle", "my granddad", "my gran", "my nana", "my nana's best friend")
sent5 <- c()
sent6 <- c()
```


## News Coverage of the `r city_name` <i>Legionella</i> outbreak

```{r news, echo=FALSE}

adj3 <- c("Disgraceful", "Terrible", "Horrible", "Devastating", "Sad", "Bloody")
emotion2 <- c("outraged", "upset", "extremely vexed", "so angry", "devastated")
sent7 <- c()
wish2 <- c("hope", "hope very much", "wish", "expect", "sincerely hope")
state2 <- c("dreadful state of affairs", "horrible pandemic", "all of the poor people dying", "tragedy")
time2 <- c("immediately", "very soon", "at once", "as soon as possible")
name2 <- c("Anna", "Luke", "Siobhan", "Su", "Ailidh", "Fiona", "Graham", "Madison", "Eleanor", "Rodrigo", "Kieran", "Wilson", "Anika", "Rosemary", "Alise", "Gordon", "Roman", "Karen")
verb2 <- c("devastate", "obliterate", "ruin", "destroy", "crush")
adj4 <- c("nearly", "almost", "virtually", "almost literally", "practically")
sent8 <- c()
sent9 <- c()
sent10 <- c()
sent11 <- c()
```

## Data gathered



